---
title: "Boostraping wild type data for power law model"
output: html_notebook
---

 

```{r include=FALSE}
library(readxl)
library(nloptr)
```

Experimental data
```{r}
exp_data <- read_excel("exp_data.xlsx")
```

Power law model
```{r}
lgp_pl<-function(vl,nd,ss,sig){
  if(nd<=0){
    p<-pnorm(nd-log2(vl/ss),0,sig)
  }else{
    p<-pnorm(nd-log2(vl/ss),0,sig)-pnorm(nd-1-log2(vl/ss),0,sig)
  }
  if(is.nan(p)){
    return(-Inf)
  }else{
    if(p<=0){return(-Inf)}else{return(log(p))}
    
  }
}

llk_pl<-function(ss,sig){
  lp<-mapply(lgp_pl,data$vol,data$ndiv,ss,sig)
  if(any(is.nan(lp)))
    return(-Inf)
  else
    return(sum(lp))
}

ef_pl<-function(x){
  ss<-x[1]
  sig<-x[2]
  return(-llk_pl(ss,sig))
}
```

Free parameter model likelihood function, models stating from 3 parameters free
```{r}
lgp_fp<-function(...){
  x<-list(...)
  vl<-x[[1]]
  nd<-x[[2]]
  ss<-x[[3]]
  sig<-x[[4]]
  zf<-as.numeric(x[5:length(x)])
  
  z<-c(zf,seq(length(zf),nd+1))
  if(nd<=0){
    p<-pnorm(z[1]-log2(vl/ss),0,sig)
  }else{
    p<-pnorm(z[nd+1]-log2(vl/ss),0,sig)-pnorm(z[nd]-log2(vl/ss),0,sig)
  }
  if(is.nan(p)){
    return(-Inf)
  }else{
    if(p<=0){return(-Inf)}else{return(log(p))}
    
  }
}
```


```{r}
lgp_fp(100,0,151.0743, 0.3126285, 0.6355754, 0.9142142)
```
General restriction setup
```{r}
eg0_fp<-function(x){
  zf<-x[3:length(x)]
  g0<-zf[1:(length(zf)-1)]-zf[2:length(zf)]
  return(g0)
}
```

Three parameter model wrapper for optimization
```{r}
llk_3p<-function(ss,sig,zf){
  lp<-mapply(lgp_fp,data$vol,data$ndiv,ss,sig,zf[1])
  if(any(is.nan(lp)))
    return(-Inf)
  else
    return(sum(lp))
}

ef_3p<-function(x){
  ss<-x[1]
  sig<-x[2]
  zf<-x[3:length(x)]
  return(-llk_3p(ss,sig,zf))
}

```


Four parameter model wrapper for optimization
```{r}
llk_4p<-function(ss,sig,zf){
  lp<-mapply(lgp_fp,data$vol,data$ndiv,ss,sig,zf[1],zf[2])
  if(any(is.nan(lp)))
    return(-Inf)
  else
    return(sum(lp))
}

ef_4p<-function(x){
  ss<-x[1]
  sig<-x[2]
  zf<-x[3:length(x)]
  return(-llk_4p(ss,sig,zf))
}
```

Five parameter model wrapper for optimization
```{r}
llk_5p<-function(ss,sig,zf){
  lp<-mapply(lgp_fp,data$vol,data$ndiv,ss,sig,zf[1],zf[2],zf[3])
  if(any(is.nan(lp)))
    return(-Inf)
  else
    return(sum(lp))
}

ef_5p<-function(x){
  ss<-x[1]
  sig<-x[2]
  zf<-x[3:length(x)]
  return(-llk_5p(ss,sig,zf))
}
```

Six parameter model wrapper for optimization
```{r}
llk_6p<-function(ss,sig,zf){
  lp<-mapply(lgp_fp,data$vol,data$ndiv,ss,sig,zf[1],zf[2],zf[3],zf[4])
  if(any(is.nan(lp)))
    return(-Inf)
  else
    return(sum(lp))
}

ef_6p<-function(x){
  ss<-x[1]
  sig<-x[2]
  zf<-x[3:length(x)]
  return(-llk_6p(ss,sig,zf))
}
```

Seven parameter model wrapper for optimization
```{r}
llk_7p<-function(ss,sig,zf){
  lp<-mapply(lgp_fp,data$vol,data$ndiv,ss,sig,zf[1],zf[2],zf[3],zf[4],z[5])
  if(any(is.nan(lp)))
    return(-Inf)
  else
    return(sum(lp))
}

ef_7p<-function(x){
  ss<-x[1]
  sig<-x[2]
  zf<-x[3:length(x)]
  return(-llk_7p(ss,sig,zf))
}
```

Optimization
```{r}
loglv<- data.frame(matrix(ncol = 6, nrow = 0))
colnames(loglv)<-c("llk_pl","llk_3p","llk_4p","llk_5p","llk_6p","llk_7p")
for(i in 1:1000){
  data<-exp_data
  data<-data[sample(nrow(data),nrow(data),replace = TRUE),]
  
  #Power law model search
  res<-nloptr(x0=c(169.9803,0.5120379),
              eval_f = ef_pl,
              lb=c(50,0.1),
              ub=c(500,0.9),
              opts = list("algorithm"="NLOPT_LN_COBYLA",
              "xtol_rel"=1.0e-2,"maxeval"=10000))
  
  
  loglv[[nrow(loglv)+1,1]]=res$objective
  
  #Three parameter model search
  res<-nloptr(x0=c(146.6109, 0.3111617, 0.7004865),
              eval_f = ef_3p,
              lb=c(50,0.1,0),
              ub=c(500,0.9,1),
              opts = list("algorithm"="NLOPT_LN_COBYLA",
              "xtol_rel"=1.0e-2,"maxeval"=10000))
  
  loglv[[nrow(loglv),2]]=res$objective
  
  #Four parameter model search
  res<-nloptr(x0=c(100,0.2,0.1,1.1),
              eval_f = ef_4p,
              eval_g_ineq = eg0_fp,
              lb=c(50,0.2,0,0),
              ub=c(500,0.9,1.5,2.5),
              opts = list("algorithm"="NLOPT_LN_COBYLA",
              "xtol_rel"=1.0e-2,"maxeval"=10000))
  
  loglv[[nrow(loglv),3]]=res$objective
  
  #Five parameter model search
  res<-nloptr(x0=c(100,0.2,0,1,2),
              eval_f = ef_5p,
              eval_g_ineq = eg0_fp,
              lb=c(50,0.1,0,0.5,1.5),
              ub=c(500,0.9,1.5,2.5,3.5),
              opts = list("algorithm"="NLOPT_LN_COBYLA",
              "xtol_rel"=1.0e-2,"maxeval"=10000))
  
  loglv[[nrow(loglv),4]]=res$objective
  
  #Six parameter model search
  res<-nloptr(x0=c(100,0.2,0.1,1.1,2.1,3),
              eval_f = ef_6p,
              eval_g_ineq = eg0_fp,
              lb=c(50,0.0,0,0.5,1.5,2.5),
              ub=c(500,0.9,1.5,2.5,3.5,4.5),
              opts = list("algorithm"="NLOPT_LN_COBYLA",
              "xtol_rel"=1.0e-2,"maxeval"=10000))
  
  loglv[[nrow(loglv),5]]=res$objective
  
  #Seven parameter model search
  res<-nloptr(x0=c(100,0.2,0.1,1.1,2.1,3,4),
              eval_f = ef_6p,
              eval_g_ineq = eg0_fp,
              lb=c(50,0.0,0,0.5,1.5,2.5,3.5),
              ub=c(500,0.9,1.5,2.5,3.5,4.5,5.5),
              opts = list("algorithm"="NLOPT_LN_COBYLA",
              "xtol_rel"=1.0e-2,"maxeval"=10000))
  
  loglv[[nrow(loglv),6]]=res$objective
}
```

```{r}
write.csv(loglv,"boot_wt_cmp_r3.csv")
```